Widening income gaps and the shrinking of the middle class

### 2024-04-02 paper/paper.qmd
Updated subtitle

---
title: "Widening income gaps and the shrinking of the middle class"
subtitle: "An analysis of the effects of various economic policies in the United States on the standards of living of middle and lower income households."
author: 
  - Abbass Sleiman
thanks: "Code and data are available at: [https://github.com/AbbassSleiman/US-Middle-Class](https://github.com/AbbassSleiman/US-Middle-Class)."
date: today
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1.2in
    abstract: ""
    number-sections: true
output: 
  bookdown::pdf_document2
toc: true
bibliography: references.bib
---

>>>>

---
title: "Widening income gaps and the shrinking of the middle class"
subtitle: "An analysis of the impact of economic policies on the living standards of middle and lower-income households amidst rising costs and affordability challenges."
author: 
  - Abbass Sleiman
thanks: "Code and data are available at: [https://github.com/AbbassSleiman/US-Middle-Class](https://github.com/AbbassSleiman/US-Middle-Class)."
date: today
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1.2in
    abstract: ""
    number-sections: true
output: 
  bookdown::pdf_document2
toc: true
bibliography: references.bib
---
